Detecting Treatment-Subgroup Interactions in Clustered Data with Generalized Linear Mixed-Effects Model Trees

### 2017-05-01 pkg/glmertree/paper/treatment_interactions.Rnw
additional remarks about the tutorial (vignette to-be)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1296 255f4249-2263-4417-b1ea-8498779e27a7

@@

The main functions in the \verb|glmertree| package are \verb|lmtree()|, for continuous outcome variables, and \verb|glmertree()|, for binary or count outcome variables. Both functions require the user to specify at least two arguments: \verb|formula| and \verb|data|. The data we will be using is the motivating example dataset described in the previous section. This dataset is included in the \verb|partykit| package and can be loaded as follows:

@@

The predictions of the random effects can be plotted by adding \verb|plotranef = TRUE| to the function call:

>>>>

\readme{This tutorial should be turned into a vignette and then the R output, graphics, etc. should be shown as well.}

@@

The main functions in the \verb|glmertree| package are \verb|lmertree()|, for continuous outcome variables, and \verb|glmertree()|, for binary or count outcome variables. Both functions require the user to specify at least two arguments: \verb|formula| and \verb|data|. The data we will be using is the motivating example dataset described in the previous section. This dataset is included in the \verb|partykit| package and can be loaded as follows:

@@

The predictions of the random effects can be plotted by adding \verb|plotranef = TRUE| to the function call:
\readme{As already indicated by e-mail, plotranef is an awkward name and should be improved, e.g., to which.}
